Union and Intersection Contracts Are Hard, Actually

### 2021-09-16 paper.tex
Add negative margins to listings to avoid reaching into margins

\lstset{
  escapeinside={(*@}{@*)}, % escape sequence to insert latex
  numbers=none % for the camera-ready version: numbers overlap with margins
}
\newcommand{\nickel}[1]{\lstinline[language=nickel]{#1}}
\newcommand{\racket}[1]{\lstinline[language=racket]{#1}}
\newcommand{\haskell}[1]{\lstinline[language=Haskell]{#1}}
\newcommand{\typescript}[1]{\lstinline[language=JavaScript]{#1}}
\newcommand{\python}[1]{\lstinline[language=Python]{#1}}

>>>>

\lstset{
  escapeinside={(*@}{@*)}, % escape sequence to insert latex
  numbers=none, % for the camera-ready version: numbers overlap with margins
  % Avoid overlap with margins
  framexleftmargin = -2pt,
  framexrightmargin = -2pt,
  framextopmargin = -2pt,
  framexbottommargin = -2pt
}

\newcommand{\nickel}[1]{\lstinline[language=nickel]{#1}}
\newcommand{\racket}[1]{\lstinline[language=racket]{#1}}
\newcommand{\haskell}[1]{\lstinline[language=Haskell]{#1}}
\newcommand{\typescript}[1]{\lstinline[language=JavaScript]{#1}}
\newcommand{\python}[1]{\lstinline[language=Python]{#1}}
